Fifteen years of decentralization attempts

### 2014-03-23 paper.tex
Added a subsection about the content on tor

>>>>

		\subsection{The content on Tor}
			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services. Illegal content and services such as drugs trading or child pornography, is a serious problem Tor is facing. A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs. This market operated as a hidden Tor service. These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.

			The illegal content travels unencrypted through a Tor exit node. Users running a Tor exit node, could be held responsible for distributing illegal content. A possible solution could be to filter the illegal content from the legal content. While content filtering is a viable solution, not many research has been done on it. It is also an open question whether filtering content is in line with the principles of Tor and the internet.
